Paper Analysis

### 2025-04-23 Paper_WriteUp/Paper_Plots.qmd
updating x axis scales in fig 3

library(tidyverse)
library(RcppRoll)
library(cmdstanr)
library(posterior)
library(bayesplot)
library(loo)
library(scales)
library(ggridges)
library(here)
library(ggdist)
library(viridis)
library(PlayerRatings)
library(ggrepel)
library(ggpubr)
library(rstanarm)
options(mc.cores = parallel::detectCores())
theme_set(theme_bw())

@@

comp_global = bind_rows(pars_17_19, pars_20_22, pars_23_25, pars_gm) |> 
  ggplot(aes(x = value, y = name, color = factor(model, levels = c("1700-1900", "2000-2200", "2300-2500", "GM")))) +
  stat_pointinterval(position = position_dodge(width = 0.2)) +
  facet_wrap(~name,
             scales = "free",
             labeller = labeller(name = facet_labels)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_3col() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "H")

# ggsave(plot = comp_global, 
#        filename = paste0(here("Paper_WriteUp", "paper_figures", "fig3.png")), dpi = 600,
#        height = 5, width = 7)
```

@@

#plotting
mu_beta_plot = mu_beta_draws %>% ggplot(aes(y = true_mu_beta, x = draw, colour = num_games)) +
  stat_pointinterval(position = ggstance::position_dodgev(height = 0.5)) +
  geom_segment(data = true_mu_betas_plotting,
               aes(x = true_val, xend = true_val, y = ymin, yend = ymax),
               color = "red", linewidth = 1.25) +
  labs(x = "Estimated Experiential Effect", y = "True mu_beta Value", colour = "Number of Games\nPlayed per Player") +
  theme_single_y_legend() +
  scale_x_continuous(breaks = c(signif(true_mu_betas, 3)), 
                     labels = c(as.character(signif(true_mu_betas, 3)))) +
  scale_color_viridis_d(option = "D")
mu_beta_plot

>>>>

library(tidyverse)
library(RcppRoll)
library(cmdstanr)
library(posterior)
library(bayesplot)
library(loo)
library(scales)
library(ggridges)
library(here)
library(ggdist)
library(viridis)
library(PlayerRatings)
library(ggrepel)
library(ggpubr)
library(rstanarm)
library(ggh4x)
options(mc.cores = parallel::detectCores())
theme_set(theme_bw())

@@

comp_global = bind_rows(pars_17_19, pars_20_22, pars_23_25, pars_gm) |> 
  ggplot(aes(x = value, y = name, color = factor(model, levels = c("1700-1900", "2000-2200", "2300-2500", "GM")))) +
  stat_pointinterval(position = position_dodge(width = 0.2)) +
  facet_wrap(~name,
             scales = "free",
             labeller = labeller(name = facet_labels)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_3col() +
  theme(legend.position = "bottom") +
  facetted_pos_scales(x = list( #for customising scales on each facet
    name == "mu_beta" ~ scale_x_continuous(breaks = c(-0.15, 0, 0.15), limits = c(-0.17, 0.17)),
    name == "gamma1" ~ scale_x_continuous(breaks = breaks_pretty(n = 2)),
    name == "gamma2" ~ scale_x_continuous(breaks = breaks_pretty(n = 2))
  )) +
  scale_color_viridis_d(option = "H")

ggsave(plot = comp_global,
       filename = paste0(here("Paper_WriteUp", "paper_figures", "fig3.png")), dpi = 600,
       height = 5, width = 7)
```

@@

#plotting
mu_beta_plot = mu_beta_draws %>% ggplot(aes(y = true_mu_beta, x = draw, colour = num_games)) +
  stat_pointinterval(position = ggstance::position_dodgev(height = 0.5)) +
  # geom_segment(data = true_mu_betas_plotting,
  #              aes(x = true_val, xend = true_val, y = ymin, yend = ymax),
  #              color = "red", linewidth = 1.25) +
  labs(x = "Estimated Experiential Effect", y = "True mu_beta Value", colour = "Number of Games\nPlayed per Player") +
  geom_vline(aes(xintercept = 0), col = "black", linetype = "dashed") +
  theme_single_y_legend() +
  scale_x_continuous(breaks = c(0, signif(true_mu_betas, 3)), 
                     labels = c(0, as.character(signif(true_mu_betas, 3)))) +
  scale_color_viridis_d(option = "D")
mu_beta_plot
